Effect of metabolic state on \textit{Paraclostridium bifermentans} surface properties and the implications for lead removal

### 2021-10-25 Writeup/Catalysts/MDPI_template/template.tex
Beefed up the introduction by adding background on why Pb is bad, what is currently being done to treat Pb, progress on the B consortium

Pb(II) is a highly soluble, mobile, and toxic pollutant that continues to cause a variety of human health problems. Exposure to Pb(II) can cause significant harm to most organs \cite{Tong2000}. The transformation of Pb(II) into a less mobile, insoluble precipitate greatly 
 is conventionally achieved with electrochemical treatment and chemical precipitation \cite{Fu2011}.

A promising alternative to conventional technology for the removal of aqueous Pb(II) is bioremediation, where organisms are used to remove or detoxify the heavy metal \cite{Philp2005}. Bioremediation is attractive due to the variety of biomaterials applicable (such as algae, fungi, plants, and bacteria) and its potential for low cost and high efficiency operation at low Pb(II) concentrations \cite{Kang2015}. Pb(II) removal with organisms has mostly been limited to sorption with biomass \cite{Chatterjee2012}, the use of plants for phytoextraction \cite{Shakoor2013}, and fungi for mycelial biosorption \cite{Chakraborty2013}. Some microorganisms have been discovered that reduce the bioavailability and toxicity of Pb(II) by precipitating it out as an insoluble complex.

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, that has been shown to remove Pb(II) from solution \cite{Brink2017}. This lead-resistant consortium has been the subject of many investigations in the pursuit of better understanding the removal mechanisms and possible implementations in the bioremediation and biorecovery of lead in industrial effluent. This includes studies on the influence of lead concentrations \cite{Brink2017,Peens2018d}, substrate concentration \cite{Brink2017,Brink2018}, precipitate identification \cite{Brink2019a,Peens2018}, influence of other divalent heavy metals \cite{Horstmann2020}, and operation in an upward anaerobic sludge bed reactor \cite{Chimhundi2021}.

Consortium precipitates PbO aerobic and PbS + PbO anaerobic, oxidation-reduction mechanism where Pb(II) acts as terminal electron acceptor \cite{Brink2020}

Modelled with fast and then slow stages \cite{Horstmann2020c}, where the fast has been attributed to biosorption \cite{Horstmann2020a}. The role of biosorption also displayed in dead bacteria \cite{VanVeenhuyzen2021}

\cite{Horstmann2020a} \textit{Paraclostridium bifermentans} and \textit{Klebsiella pneumoniae}

@@

The chemical composition of bacteria surfaces for both Gram-positive and Gram-negative bacteria are rich in negatively charged functional groups that result in an overall negative surface charge and facilitate the attraction of positively charged metal cations like ionic lead \cite{Vijayaraghavan2008}. These functional groups also allow for chemisorption to take place, where hydrogen ions are exchanged for Pb(II)
ions (Lu et al., 2012) \cite{Lu2012}.
Chemisorption not only prevents lead from entering cells, but 
Functional
group complexation can be a prominent adsorption mechanism for some bacteria
that use it to concentrate terminal electron accepting ions on the cell wall surface

\cite{Haas2001}

@@

>>>>

% Lead as a problem and how it is fixed

Pb(II) is a highly water-soluble, mobile, and toxic pollutant that continues to cause a variety of human health problems. Chronic exposure to Pb(II) causes significant harm to most organs \cite{Tong2000}. The conversion of Pb(II) into insoluble precipitates can, however, greatly reduce its mobility and toxicity \cite{Zeng2017}. This is conventionally achieved with electrochemical treatment and chemical precipitation \cite{Fu2011}. Bioprecipitation with microbes has gained attention as a promising method to immobilize aqueous Pb(II) as lead phosphate \cite{Levinson1996, Naik2013c}, lead sulfide \cite{De2008}, or elemental lead \cite{Amer2022}.

% Enter: the B-culture

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, and has been shown to remove up to 93~\% of Pb(II) from solution \cite{Brink2017} by precipitating it out as PbS and Pb(0) \cite{Brink2020}. Following kinetic studies on the consortium, H\"orstmann et al. \cite{Horstmann2020c} proposed a two-phase exponential decay model to describe Pb(II) removal and attributed an initial rapid phase to adsorption. Subsequent research built on this proposal by demonstrating that significant Pb(II) removal with the consortium took place following sterilization with NaN\textsubscript{3} \cite{VanVeenhuyzen2021}, highlighting the involvement of adsorption as a rather than the metabolically dependent precipitation.

% Adsorption and bacteria

@@

The chemical composition of bacteria surfaces for both Gram-positive and Gram-negative bacteria are rich in negatively charged functional groups that result in an overall negative surface charge and facilitate the attraction of positively charged metal cations like ionic lead \cite{Vijayaraghavan2008}. These functional groups also allow for chemisorption to take place, where hydrogen ions are exchanged for Pb(II)
ions \cite{Lu2012}.
Chemisorption not only prevents lead from entering cells, but 
Functional
group complexation can be a prominent adsorption mechanism for some bacteria
that use it to concentrate terminal electron accepting ions on the cell wall surface

@@

% Titrations
